landlord

### 2023-06-07 src/01_metric_normalization.Rmd
read csv instead of xlsx file

anchor_city <- read.xlsx(here("data/intermediate/demographic_data.xlsx"), sheetName="anchor_city") %>% 
  clean_names() %>% 
   inner_join(city_occupancy_data, by = join_by(cbsa== cbsa, anchor_city==city)) %>% 
  select(cbsa, anchor_city, occ_rate2021)

>>>>

anchor_city <- read_csv(here("data/intermediate/demographic_data.csv")) %>% 
  clean_names() %>% 
   inner_join(city_occupancy_data, by = join_by(cbsa== cbsa, anchor_city==city)) %>% 
  select(cbsa, anchor_city, occ_rate2021)
